---
title: "R-Vignette"
author: "Jelly BeanR"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R-Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(chess.analytics)
```


In this tutorial, we are going to showcase some of the functions that this package provides. Chess is a well known game that has been around for centuries. Chess involves two teams, White and Black. Each player has a King, Queen, two bishops, two knights, two rooks, and 8 pawns.  The objective is to have one a piece attacking the opposing team's king and they have not options to move the king out of an attack or defend with any of their other pieces. 

## Background Information and goals

The goal of this package is to take information from the Kaggle Lichess dataset. This package takes their csv of all the data and stores the data in a different data structure.  This allows the user to put in a game number and have access to functions such as: plotting a chess game, visualizing the game score, and creating a heatmap on where a certain piece dies.



## Figures of how to plot a game and game_score

The figure sizes have been customized so that you can easily put two images side-by-side. 

```{r, warning=FALSE}
# p1 <- function(x, knitr = FALSE){
#   plot(x)
#   if(!knitr) dev.new()
#   plot(x^2)
# }
# chess.analytics::plot_game(1, .1)
plot_score()

```


